---
title: 'Regression results for smoking status'
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---

This document contains the summaries of the regression analyses with smoking status as the outcome and all covariates included. We provide the code used to generate this table, which calls upon our analysis summary objects (also provided).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```


```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(papaja)
library(tidyverse)
library(tools)
library(psych)
library(knitr)
library(kableExtra)
library(here)
```

```{r load_data, results='hide', echo = F}
study.names = c("BASEII", "EAS","ELSA", "HRS", "ILSE", "LBC",
                "LBLS", "MAP", "MAS","MIDUS","NAS", "OATS", 
                "ROS","SLS","WLS")

lapply(here(paste0("behavior/", study.names, "_behavior.Rdata")), load, .GlobalEnv)
```

```{r identify, echo = F}
#identify which studies have active outcome
smoker.names = lapply(paste0(study.names,"_behavior"), 
                      FUN = function(x) rownames(get(x)$descriptives))
smoker.names = sapply(smoker.names, FUN = function(x) "smoker" %in% x)
smoker.names = study.names[smoker.names]
```

```{r columns, echo = F}
columns = unite(
  expand.grid(stat = c("estimate", "std.error", "OR", "statistic", "p.value"),
              study = smoker.names),
  columns, study, stat, sep="_")$columns
```

```{r header, echo = F}
header = c(" " = 1, "BASEII" = 5, "EAS" = 5, "ELSA" = 5, "HRS" = 5, "ILSE" = 5, 
           "LBLS" = 5, "LBC" = 5, "MAP" = 5, "MAS" = 5, "MIDUS" = 5, "NAS" = 5, "OATS" = 5,  
           "ROS" = 5, "SLS" = 5, "WLS" = 5)
```


# Main Effects

```{r main, message = FALSE, warning = FALSE, results='asis', echo = F}
#sample size
smoker.n = data.frame(study = smoker.names, 
                      term = "N", estimate = 
                        sapply(X = smoker.names, FUN = function(x)
                          get(paste0(x,"_behavior"))$regression$main$smoker$n)) %>%
  mutate(study = paste0(study, "_estimate")) %>%
  spread(key = "study", value = "estimate")

lapply(X = smoker.names, FUN = function(x) get(paste0(x,"_behavior"))$regression$main$smoker$coef) %>%
  map2_df(., smoker.names, ~ mutate(.x, study = .y)) %>%
  mutate(OR = exp(estimate)) %>%
  gather(key = "key", value = "value", -study, -term) %>%
  unite(study_stat, study, key, sep="_") %>%
  filter(!is.infinite(value)) %>%
  spread(key = "study_stat", value = "value") %>%
  gather(key = "key", value = "value", which(grepl("p", names(.)))) %>%
  filter(!is.na(value)) %>%
  mutate(sig = value, 
    value = printp(value),
    value = cell_spec(value, "html", 
                      color = ifelse(sig >= .05 | is.na(sig), 
                                     "black", "red"))) %>%
    filter(!grepl("NA", value))%>%
    dplyr::select(-sig) %>%
    spread(key = "key", value = "value") %>%
    full_join(smoker.n) %>%
    mutate(term = gsub("\\(", "", term), 
           term = gsub("\\)", "", term),
           term = toTitleCase(term),
           term = gsub("\\:", " x ", term), 
          term = factor(term, 
                         levels = c("Intercept", "Age", "Gender", "Edu", "Agree", "Extra", "Open", 
                                    "Neur", "Con", "Neur x con", "N"))) %>%
    arrange(term) %>%
    dplyr::select(term, columns) %>%
    kable(.,  booktabs = T, escape = F, digits = 2, format = "html", 
          align=c(rep('c',times=ncol(.))),
          col.names = c("Term", rep(c("Est","SE","OR", "t value", "p"), length(smoker.names)))) %>%
    kable_styling("bordered", full_width = TRUE) %>%
  add_header_above(header = header) 
```

# Interaction, no covariates


```{r interaction, message = FALSE, warning = FALSE, results='asis', echo = F}
#sample size
smoker.n = data.frame(study = smoker.names, 
                      term = "N", estimate = 
                        sapply(X = smoker.names, FUN = function(x)
                          get(paste0(x,"_behavior"))$regression$intr$smoker$n)) %>%
  mutate(study = paste0(study, "_estimate")) %>%
  spread(key = "study", value = "estimate")

lapply(X = smoker.names, FUN = function(x) get(paste0(x,"_behavior"))$regression$intr$smoker$coef) %>%
  map2_df(., smoker.names, ~ mutate(.x, study = .y)) %>%
  mutate(OR = exp(estimate)) %>%
  gather(key = "key", value = "value", -study, -term) %>%
  unite(study_stat, study, key, sep="_") %>%
  filter(!is.infinite(value)) %>%
  spread(key = "study_stat", value = "value") %>%
  gather(key = "key", value = "value", which(grepl("p", names(.)))) %>%
  filter(!is.na(value)) %>%
  mutate(sig = value, 
    value = printp(value),
    value = cell_spec(value, "html", 
                      color = ifelse(sig >= .05 | is.na(sig), 
                                     "black", "red"))) %>%
    filter(!grepl("NA", value))%>%
    dplyr::select(-sig) %>%
    spread(key = "key", value = "value") %>%
    full_join(smoker.n) %>%
    mutate(term = gsub("\\(", "", term), 
           term = gsub("\\)", "", term),
           term = toTitleCase(term),
           term = gsub("\\:", " x ", term), 
           term = factor(term, 
                       levels = c("Intercept", "Age", "Gender", "Edu", "Agree", "Extra", "Open", 
                                  "Neur", "Con", "Neur x con", "N"))) %>%
  arrange(term) %>%
  dplyr::select(term, columns) %>%
  kable(.,  booktabs = T, escape = F, digits = 2, format = "html", 
        align=c(rep('c',times=ncol(.))),
        col.names = c("Term", rep(c("Est","SE","OR", "t value", "p"), length(smoker.names)))) %>%
  kable_styling("bordered", full_width = TRUE) %>%
add_header_above(header) 
```

# Interaction, demographics

```{r demo, message = FALSE, warning = FALSE, results='asis', echo = F}
#sample size
smoker.n = data.frame(study = smoker.names, 
                      term = "N", estimate = 
                        sapply(X = smoker.names, FUN = function(x)
                          get(paste0(x,"_behavior"))$regression$cov1$smoker$n)) %>%
  mutate(study = paste0(study, "_estimate")) %>%
  spread(key = "study", value = "estimate")

lapply(X = smoker.names, FUN = function(x) get(paste0(x,"_behavior"))$regression$cov1$smoker$coef) %>%
  map2_df(., smoker.names, ~ mutate(.x, study = .y)) %>%
  mutate(OR = exp(estimate)) %>%
  gather(key = "key", value = "value", -study, -term) %>%
  unite(study_stat, study, key, sep="_") %>%
  filter(!is.infinite(value)) %>%
  spread(key = "study_stat", value = "value") %>%
  gather(key = "key", value = "value", which(grepl("p", names(.)))) %>%
  filter(!is.na(value)) %>%
  mutate(sig = value, 
    value = printp(value),
    value = cell_spec(value, "html", 
                      color = ifelse(sig >= .05 | is.na(sig), 
                                     "black", "red"))) %>%
    filter(!grepl("NA", value))%>%
    dplyr::select(-sig) %>%
    spread(key = "key", value = "value") %>%
    full_join(smoker.n) %>%
    mutate(term = gsub("\\(", "", term), 
           term = gsub("\\)", "", term),
           term = toTitleCase(term),
           term = gsub("\\:", " x ", term), 
           term = factor(term, 
                         levels = c("Intercept", "Age", "Gender", "Edu", "Agree", "Extra", "Open", 
                                    "Neur", "Con", "Neur x con", "N"))) %>%
    arrange(term) %>%
    dplyr::select(term, columns) %>%
    kable(.,  booktabs = T, escape = F, digits = 2, format = "html", 
          align=c(rep('c',times=ncol(.))),
          col.names = c("Term", rep(c("Est","SE","OR", "t value", "p"), length(smoker.names)))) %>%
    kable_styling("bordered", full_width = TRUE) %>%
  add_header_above(header)  
```

# Interaction, all covariates

```{r all_cov, message = FALSE, warning = FALSE, results='asis', echo = F}
#sample size
smoker.n = data.frame(study = smoker.names, 
                      term = "N", estimate = 
                        sapply(X = smoker.names, FUN = function(x)
                          get(paste0(x,"_behavior"))$regression$cov2$smoker$n)) %>%
  mutate(study = paste0(study, "_estimate")) %>%
  spread(key = "study", value = "estimate")

lapply(X = smoker.names, FUN = function(x) get(paste0(x,"_behavior"))$regression$cov2$smoker$coef) %>%
  map2_df(., smoker.names, ~ mutate(.x, study = .y)) %>%
  mutate(OR = exp(estimate)) %>%
  gather(key = "key", value = "value", -study, -term) %>%
  unite(study_stat, study, key, sep="_") %>%
  filter(!is.infinite(value)) %>%
  spread(key = "study_stat", value = "value") %>%
  gather(key = "key", value = "value", which(grepl("p", names(.)))) %>%
  filter(!is.na(value)) %>%
  mutate(sig = value, 
    value = printp(value),
    value = cell_spec(value, "html", 
                      color = ifelse(sig >= .05 | is.na(sig), 
                                     "black", "red"))) %>%
  filter(!grepl("NA", value)) %>%
  dplyr::select(-sig) %>%
  spread(key = "key", value = "value") %>%
  full_join(smoker.n) %>%
  mutate(term = gsub("\\(", "", term), 
         term = gsub("\\)", "", term),
         term = toTitleCase(term),
         term = gsub("\\:", " x ", term), 
         term = factor(term, 
                       levels = c("Intercept", "Age", "Gender", "Edu", "Agree", "Extra", "Open", 
                                  "Neur", "Con", "Neur x con", "N"))) %>%
  arrange(term) %>%
  dplyr::select(term, columns) %>%
  kable(.,  booktabs = T, escape = F, digits = 2, format = "html", 
        align=c(rep('c',times=ncol(.))),
        col.names = c("Term", rep(c("Est","SE","OR", "t value", "p"), length(smoker.names)))) %>%
  kable_styling("bordered", full_width = TRUE) %>%
add_header_above(header) 
```

```{r paste, echo = FALSE, eval = FALSE}
cat("header = c(\" \" = 1,", paste0("\"", smoker.names, "\" ", "= 4", collapse = ", "), ")")
```

# Code

## Preparation

The following packages were used to generate this table: 

```{r ref.label = "load_packages", warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.


First we load the individual study analysis objects.

```{r ref.label = "load_data", results='hide', eval = F}
```

Then we identify which studies have smoking as an outcome.

```{r ref.label = "identify", eval = F}
```

```{r ref.label = "columns", eval = F}
```

```{r ref.label = "header", eval = F}
```


## Main Effects

```{r ref.label = "main", message = FALSE, warning = FALSE, results='asis', eval = F}
```

## Interaction, no covariates


```{r ref.label = "interaction", message = FALSE, warning = FALSE, results='asis', eval = F}
```

## Interaction, demographics

```{r ref.label = "demo", message = FALSE, warning = FALSE, results='asis', eval = F}
```

## Interaction, all covariates

```{r ref.label = "all_cov", message = FALSE, warning = FALSE, results='asis', eval = F}
```


