---
title: 'Predicted Values: Alcohol consumption status'
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---

This document contains the plot of predicted probabilities from each individual study, as well as the weighted average effect, from the cross-sectional analyses.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(tidyverse)
library(metafor)
library(here)
```

```{r load_data, echo = F}
load(here("behavior/created data/plot_drinker.Rdata"))
```

```{r plot, fig.height= 9, echo = F}
drinker.plot %>%
  ggplot(aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin=lower, ymax=upper), fill="black", alpha=.15,
              data = weighted.vals)+
  geom_line(aes(color = study), lty="dashed") +
  geom_line(data = weighted.vals, color="black") +
  facet_wrap(~group) +
  theme_bw() +
  theme(legend.position = "bottom")
```

# Code

The following packages were used to generate this figure: 

```{r ref.label = "load_packages", warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Meta Analysis Output folder.

First we load the meta-analysis objects. To see how these objects were created, see the meta-analysis scripts titled `drinker_meta-analysis.R` that are available at [osf.io/kb9e8](https://osf.io/kb9e8/).

```{r ref.label = "load_data", eval = F}
```

We plot the values.

```{r ref.label = "plot", fig.height= 9, eval = F}
```

