---
title: "Meta analysis of main effects (time since baseline as metric)"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---
This document contains the meta-analysis of the surivival models, using time since baseline as the metric of interest and neuroticism by conscientiousness as the predictor of interest.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```


```{r load_packages, echo = F, warning = FALSE, message = FALSE, results = 'hide'}
library(papaja)
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
library(here)
```

```{r load_data, echo = F, results = 'hide'}
study.names = c("EAS", "HRS", "LBC", "LBLS", "MAP", "MAS", "MIDUS", "NAS", "OATS", "ROS", "SLS", "WLS")
lapply(here(paste0("mortality/study output/", study.names, "_survival_output.Rdata")), load, .GlobalEnv)
```

```{r extract, echo = F}
meta.data.time <- data.frame()

n <- 0

for(i in study.names){
  n <- n+1
  x <- get(paste0(i, "_survival_output"))
  meta.data.time[n, "study"] <- i
  meta.data.time[n, "n_coef"] <- x$time$model1$coef["z.neur", "coef"]
  meta.data.time[n, "n_se"] <- x$time$model2$coef["z.neur", "se(coef)"]
  meta.data.time[n, "c_coef"] <- x$time$model1$coef["z.con", "coef"]
  meta.data.time[n, "c_se"] <- x$time$model2$coef["z.con", "se(coef)"]
  meta.data.time[n, "n"] <- x$time$model2$ntotal
  meta.data.time[n, "n_died"] <- x$descriptives$died.tab["1"]
}

meta.results.time.neur <- rma(yi = n_coef, 
                              sei = n_se, 
                              ni = n,  
                              measure = "RR",
                              slab = study, 
                              data = meta.data.time)

meta.results.time.con <- rma(yi = c_coef, 
                              sei = c_se, 
                              ni = n,  
                              measure = "RR",
                              slab = study, 
                              data = meta.data.time)

meta.data.time = meta.data.time %>%
  gather("key", "value", n_coef, n_se, c_coef, c_se) %>%
  separate("key", into = c("trait", "key")) %>%
  spread("key", "value")

meta.results.time = rma(yi = coef, 
                        sei = se, 
                        ni = n,  
                        measure = "RR",
                        slab = study, 
                        data = meta.data.time)
```


```{r bounds, echo = F}
meta.data.time = meta.data.time %>%
  #mutate(study = gsub("LBC", "LBC1936", study)) %>%
  arrange(trait, study)

#find plot limits
max.ci = meta.data.time %>%
  mutate(ci = exp(coef+1.96*se)) %>%
  arrange(desc(ci))
max.ci = max.ci[2, "ci"]

#max.ci = max(exp(neur.data$estimate+1.96*neur.data$se))
min.ci = min(exp(meta.data.time$coef-1.96*meta.data.time$se))

range = max.ci-min.ci

lower = min.ci-(range)
upper = max.ci+(range)*.5

#estimate position of extra information
pos = min.ci-lower
pos = pos/2
pos = c(lower+.8*pos, lower+1.6*pos)

unique = nrow(meta.data.time)/2
rows = c(1:unique, (unique+6):((2*unique)+5))
cex.set = .65

forest(meta.data.time$coef, meta.data.time$se^2,
       cex = cex.set,
       slab = meta.data.time$study,
       xlim = c(lower, upper),
       alim = c(min.ci, max.ci),
       transf=exp,
       rows = rows[order(rows,decreasing = T)],
       ylim = c(-1, 5+max(rows)),
       refline = 1,
       ilab = meta.data.time[,c("n", "n_died")],
       ilab.xpos = pos)

addpoly(meta.results.time.con, row = unique+5, 
        cex = cex.set,transf =exp, mlab="", col = "blue")
addpoly(meta.results.time.neur, row = min(rows)-1, 
        cex = cex.set,transf =exp, mlab="", col = "blue")

text(lower, unique+5, pos=4, cex = cex.set,
     bquote(paste("(Q = ",
                  .(formatC(meta.results.time.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.results.time.con$k - meta.results.time.con$p),
                  ", p = ", .(formatC(meta.results.time.con$QEp, digits=2, format="f")), 
                  "; ", I^2, " = ",
                  .(formatC(meta.results.time.con$I2, digits=1, format="f")), "%)")))
text(lower, min(rows)-1, pos=4, cex = cex.set,
     bquote(paste("(Q = ",
                  .(formatC(meta.results.time.neur$QE, digits=2, format="f")),
                  ", df = ", .(meta.results.time.neur$k - meta.results.time.neur$p),
                  ", p = ", .(formatC(meta.results.time.neur$QEp, digits=2, format="f")), 
                  "; ", I^2, " = ",
                  .(formatC(meta.results.time.neur$I2, digits=1, format="f")), "%)")))
text(lower, 5.5+max(rows),
     "Study", cex = cex.set*1.2, pos = 4)
text(upper, 5.5+max(rows),
     "Risk Ratio [95% CI]", cex = cex.set*1.2, pos=2)
text(lower, max(rows)+1.5,
     "Main Effect of Conscientiousness", cex = cex.set*1.1, pos = 4, font = 2)
text(lower, unique+2,
     "Main Effect of Neuroticism", cex = cex.set*1.1, pos = 4, font = 2)

```

# Code

The following packages were used to generate this table: 

```{r load_packages, echo = F, warning = FALSE, message = FALSE, results = 'hide'}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

First we load the individual study analysis objects.

```{r load_data, echo = F, results = 'hide'}
```


```{r extract, echo = F}
```


```{r bounds, echo = F}
```


