---
title: "Meta analysis of interaction with no covariates(time since baseline as metric)"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---
This document contains the meta-analysis of the surivival models, using time since baseline as the metric of interest and neuroticism by conscientiousness as the predictor of interest.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```


```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(papaja)
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
library(here)
```


```{r data_path, echo = F}
data.path = here("mortality/study output/")
```


```{r study_names, results = 'hide', echo = F}
study.names = c("EAS", "HRS","LBLS", "MAP", "MIDUS", "NAS", "ROS", "SLS", "WLS")

lapply(paste0(data.path, study.names, "_survival_output.Rdata"), load, .GlobalEnv)
```


```{r meta_analysis, echo = F}
meta.data.time <- data.frame()
n <- 0

for(i in study.names){
  n <- n+1
  x <- get(paste0(i, "_survival_output"))
  meta.data.time[n, "study"] <- i
  meta.data.time[n, "coef"] <- x$time$model0b$coef["z.neur:z.con", "coef"]
  meta.data.time[n, "se"] <- x$time$model0b$coef["z.neur:z.con", "se(coef)"]
  meta.data.time[n, "n"] <- x$time$model0b$ntotal
  meta.data.time[n, "n_died"] <- x$descriptives$died.tab["1"]

}

meta.results.time <- rma(yi = coef, 
                    sei = se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.time)
```

```{r, echo = F}
save(meta.results.time, file = here("mortality/created data/meta_time_nocov.Rdata"))
```


```{r forest_plot, echo = F}

#find plot limits
max.ci.mod1 = max(exp(meta.data.time$coef+1.96*meta.data.time$se))
min.ci.mod1 = min(exp(meta.data.time$coef-1.96*meta.data.time$se))
range.mod1 = max.ci.mod1-min.ci.mod1

lower.mod1 = min.ci.mod1-(range.mod1*2.5)
upper.mod1 = max.ci.mod1+(range.mod1*1.5)

cex.set = .7

#estimate position of extra information
pos.mod1 = min.ci.mod1-lower.mod1
pos.mod1 = pos.mod1/6
pos.mod1 = c(lower.mod1+2.5*pos.mod1,
             lower.mod1+4*pos.mod1)

meta.data.time$study = gsub("LBC", "LBC1936", meta.data.time$study)

#forest plot
forest(meta.results.time,
       xlim = c(lower.mod1, upper.mod1),
       cex = cex.set,
       slab = meta.data.time$study,
       transf=exp,
       refline = 1,
       ilab = meta.data.time[,c("n", "n_died")],
       ilab.xpos = pos.mod1)

#additional text
text(c(pos.mod1), length(study.names)+1.5,
     c("N", "Died"), cex = cex.set)
text(lower.mod1, length(study.names)+1.5,
     "Study", cex = cex.set, pos = 4)
text(upper.mod1, length(study.names)+1.5,
     "Interaction Hazard Ratio [95% CI]", cex = cex.set, pos=2)
text(lower.mod1, -1.5, pos=4, cex=cex.set, 
     bquote(paste("(Q = ",
     .(formatC(meta.results.time$QE, digits=2, format="f")), ", df = ", .(meta.results.time$k - meta.results.time$p),
     ", p = ", .(formatC(meta.results.time$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(meta.results.time$I2, digits=1, format="f")), "%)")))
```

# Code


The following packages were used to generate this table: 

```{r ref.label = "load_packages", warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

Specify the location of the study analysis objects. The first author stored these in a Box Sync folder, but you may have downloaded these to a different location. The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

```{r ref.label = "data_path", eval = F}
```

First we load the individual study analysis objects.

```{r ref.label = "study_names", results = 'hide', eval = F}
```


```{r ref.label = "meta_analysis", eval = F}
```


```{r ref.label = "forest_plot", eval = F}
```
