---
title: "Survival plots by study (time since baseline as metric)"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---
This document contains the survival plots of the surivival models, using time since baseline as the metric of interest and neuroticism by conscientiousness as the predictor of interest.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

```{r load_packages, echo = F, warning = FALSE, message = FALSE, results = 'hide'}
library(papaja)
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)
```

```{r load_data, echo = F, warning = FALSE, message = FALSE, results = 'hide'}
study.names = c("EAS", "HRS", "LBC", "LBLS", "MAP", "MAS", "MIDUS", "NAS", "OATS", "ROS", "SLS", "WLS")
lapply(here(paste0("mortality/study output/", study.names, "_survival_output.Rdata")), load, .GlobalEnv)
```

```{r extract, echo = F, warning = FALSE, message = FALSE}
plottime.s = lapply(paste0(study.names, "_survival_output"), 
                  FUN = function(x) get(x)$plotdata$time.s) %>%
  map2_df(., study.names, ~ mutate(.x, study = .y))

plot_n = data.frame(study = study.names,
                    n = sapply(paste0(study.names, "_survival_output"), 
                  FUN = function(x) get(x)$time$model2$ntotal))

plottime.s = plottime.s %>%
  full_join(plot_n)
```

```{r plot, echo = F, warning = FALSE, message = FALSE}
plottime.s %>%
  mutate(study = gsub("LBC", "LBC1936", study)) %>%
  mutate(z.neur = factor(z.neur, levels = c(-1, 1), labels = c("High Neuroticism", "Low Neuroticism")),
         z.con = factor(z.con, levels = c(-1, 1), labels = c("High Conscientiousness", "Low Conscientiousness"))) %>%
  ggplot(aes(x = time, y = probability)) +
  geom_line(aes(color = study), linetype = "dashed") +
  # stat_smooth(aes(weight = n),
  #             method = "loess",
  #             formula = y ~ x,
  #             se =  TRUE,
  #             size = 1, color = "black") + 
  scale_x_continuous("Time (in months since personality assessment)") +
  scale_y_continuous("Probability of survival") +
  facet_grid(z.neur~z.con) + 
  theme_bw() + 
  theme(legend.position = "bottom")
```

# Code

The following packages were used to generate this table: 

```{r load_packages, eval = F, warning = FALSE, message = FALSE, results = 'hide'}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

First we load the individual study analysis objects.

```{r load_data, eval = F, results = 'hide'}
```

Next we extract the predicted values from each object.

```{r extract, eval = F}
```

Finally, we plot individual values, as well as the overall weighted line. 

```{r plot, eval = F}
```
