---
title: 'Predicted Values: Longitudinal'
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---

This document contains the plot of predicted probabilities from each individual study, as well as the weighted average effect, from the long-sectional analyses.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```


```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(tidyverse)
library(metafor)
library(here)
```

```{r load_data, echo = F}
load(here("meta output/hbp_long.Rdata"))
weighted.long.hbp <- weighted.vals
load(here("meta output/diabetes_long.Rdata"))
weighted.long.diab <- weighted.vals
load(here("meta output/heart_long.Rdata"))
weighted.long.heart <- weighted.vals

rm(weighted.vals)
```


```{r merge, echo = F, message = F, warning = F}
weighted.long.hbp$outcome = "Hypertension"
weighted.long.diab$outcome = "Diabetes"
weighted.long.heart$outcome = "Heart Disease"

weighted.long.all <- weighted.long.hbp %>%
  full_join(weighted.long.diab) %>%
  full_join(weighted.long.heart) %>%
  mutate(outcome = factor(outcome, levels = c("Hypertension", "Diabetes", "Heart Disease")))

hbp.long.plot$outcome = "Hypertension"
diab.long.plot$outcome = "Diabetes"
heart.long.plot$outcome = "Heart Disease"

plot.long.all <- hbp.long.plot %>%
  full_join(diab.long.plot) %>%
  full_join(heart.long.plot) %>%
  mutate(outcome = factor(outcome, levels = c("Hypertension", "Diabetes", "Heart Disease")))
```

```{r plot, fig.height= 9, echo = F}
plot.long.all %>%
  ggplot(aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin=lower, ymax=upper), fill="black", alpha=.15,
              data = weighted.long.all)+
  geom_line(aes(color = study), lty="dashed") +
  geom_line(data = weighted.long.all, color="black") +
  scale_x_continuous("Neuroticism")+
  scale_y_continuous("Probability of \n developing chronic condition") +
  facet_grid(outcome~group)+
  theme_minimal()+
  theme(legend.position = "bottom")
```

# Code

The following packages were used to generate this figure: 

```{r ref.label = "load_packages", warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Meta Analysis Output folder.
First we load the meta-analysis objects. To see how these objects were created, see the meta-analysis scripts titled `hbp_long_sectional.R`, `diabetes_long_sectional.R`, and `heart_long_sectional.R` that are available at [osf.io/35etv](https://osf.io/35etv/).

```{r ref.label = "load_data", eval = F}
```

Next we merge the data frames from the different objects.

```{r ref.label = "merge", eval = F, message = F, warning = F}
```

Finally, we plot the values.

```{r ref.label = "plot", fig.height= 9, eval = F}
```

