---
title: "Main Effects of Conscientiousness"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---

This document organizes and summarizes the main effects of conscientiousness on health outcomes, controlling for conscientiousness, across the studies. 

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(tidyverse)
library(metafor)
library(papaja)
library(here)
```

```{r load_data, warning=FALSE, message=FALSE, echo = F}
study.names = c("BASEII", "EAS", "ELSA", "HRS", "ILSE", "LBC",
                "LBLS","MAP", "MAS", "MIDUS",
                "NAS", "OATS", "ROS", "SLS", "WLS")

load(here("created data/BASEII_cc_output_nosrh.Rdata"))
load(here("created data/EAS_cc_nosrh_output.Rdata"))
load(here("created data/ELSA_cc_output.Rdata"))
load(here("created data/HRS_cc_output.Rdata"))
load(here("created data/ILSE_cc_output_nosrh.Rdata"))
load(here("created data/LBC_cc_output.Rdata"))
load(here("created data/LBLS_cc_output.Rdata"))
load(here("created data/MAP_cc_output.Rdata"))
load(here("created data/MAS_cc_output_nosrh.Rdata"))
load(here("created data/MIDUS_cc_output_nosrh.Rdata"))
load(here("created data/nas_cc_output.Rdata"))
load(here("created data/OATS_cc_output_nosrh.Rdata"))
load(here("created data/ROS_cc_output.Rdata"))
load(here("created data/SLS_cc_output.Rdata"))
load(here("created data/WLS_cc_output.Rdata"))


NAS_cc_output = nas_cc_output
rm(nas_cc_output)
```

```{r extra_info, warning=FALSE, message=FALSE, echo = F}
# cross-sectional models

data_cross_main <- data.frame() # create empty data frame
n <- 0 # start at row 0

for(i in study.names){ # loop through studies
  n = n + 1 # increase row by 1

  x <- get(paste0(i,"_cc_output")) # get output object

  # fill in study-level data
  data_cross_main[n, "name"] <- i
  
  #extract coefficient estimates from diabetes model
    if(!is.null(x$main_effects$diabetes$cross$coef)){
        data_cross_main$con_est_diab[n] <- x$main_effects$diabetes$cross$coef["z.con", "Estimate"]
        data_cross_main$con_se_diab[n] <- x$main_effects$diabetes$cross$coef["z.con", "Std. Error"]
        data_cross_main$n_diab[n] <- x$main_effects$diabetes$cross$n
        }

  #extract coefficient estimates from high blood pressure model
  data_cross_main$con_est_hbp[n] <- x$main_effects$hbp$cross$coef["z.con", "Estimate"]
  data_cross_main$con_se_hbp[n] <- x$main_effects$hbp$cross$coef["z.con", "Std. Error"]
  data_cross_main$n_hbp[n] <- x$main_effects$hbp$cross$n

  #extract coefficient estimates from heart disease model
  if(!is.null(x$main_effects$heart$cross$coef)){
  data_cross_main$con_est_heart[n] <- x$main_effects$heart$cross$coef["z.con", "Estimate"]
  data_cross_main$con_se_heart[n] <- x$main_effects$heart$cross$coef["z.con", "Std. Error"]
  data_cross_main$n_heart[n] <- x$main_effects$heart$cross$n
  }
}

#longitudinal models

data_long_main <- data.frame() # create empty data frame
n <- 0 # start at row 0

for(i in study.names){ # loop through studies
  n = n + 1 # increase row by 1

  x <- get(paste0(i,"_cc_output")) # get output object

  # fill in study-level data
  data_long_main[n, "name"] <- i
  
  #extract coefficient estimates from diabetes model
    if(!is.null(x$main_effects$diabetes$long$coef)){
      data_long_main$con_est_diab[n] <- x$main_effects$diabetes$long$coef["z.con", "Estimate"]
      data_long_main$con_se_diab[n] <- x$main_effects$diabetes$long$coef["z.con", "Std. Error"]
      data_long_main$n_diab[n] <- x$main_effects$diabetes$long$n}
  

  #extract coefficient estimates from high blood pressure model
  data_long_main$con_est_hbp[n] <- x$main_effects$hbp$long$coef["z.con", "Estimate"]
  data_long_main$con_se_hbp[n] <- x$main_effects$hbp$long$coef["z.con", "Std. Error"]
  data_long_main$con_est_hbp[n] <- x$main_effects$hbp$long$coef["z.con", "Estimate"]
  data_long_main$con_se_hbp[n] <- x$main_effects$hbp$long$coef["z.con", "Std. Error"]
  data_long_main$n_hbp[n] <- x$main_effects$hbp$long$n

  #extract coefficient estimates from heart disease model
  if(!is.null(x$main_effects$heart$long$coef)){
    data_long_main$con_est_heart[n] <- x$main_effects$heart$long$coef["z.con", "Estimate"]
    data_long_main$con_se_heart[n] <- x$main_effects$heart$long$coef["z.con", "Std. Error"]
    data_long_main$n_heart[n] <- x$main_effects$heart$long$n
  }
}
```

```{r meta_analysis, warning=FALSE, message=FALSE, echo = F}

# high blood pressure - conscientiousness
meta.cross.hbp.con <- metafor::rma(yi = con_est_hbp,
                                    sei = con_se_hbp,
                                    ni = n_diab,
                                    measure = "OR",
                                    slab = name,
                                    method="REML",
                                    data = data_cross_main)

# diabetes - conscientiousness
meta.cross.diab.con <- metafor::rma(yi = con_est_diab,
                                     sei = con_se_diab,
                                     ni = n_diab,
                                     measure = "OR",
                                     slab = name,
                                     method="REML",
                                     data = data_cross_main)

# heart disease - conscientiousness
meta.cross.heart.con <- metafor::rma(yi = con_est_heart,
                                      sei = con_se_heart,
                                      ni = n_diab,
                                      measure = "OR",
                                      slab = name,
                                      method="REML",
                                      data = data_cross_main)

# ------ meta-analysis: longitudinal ------

# high blood pressure - conscientiousness
meta.long.hbp.con <- metafor::rma(yi = con_est_hbp,
                                   sei = con_se_hbp,
                                   ni = n_diab,
                                   measure = "OR",
                                   slab = name,
                                   method="REML",
                                   data = data_long_main)

# diabetes - conscientiousness
meta.long.diab.con <- metafor::rma(yi = con_est_diab,
                                    sei = con_se_diab,
                                    ni = n_diab,
                                    measure = "OR",
                                    slab = name,
                                    method="REML",
                                    data = data_long_main)

# heart disease - conscientiousness
meta.long.heart.con <- metafor::rma(yi = con_est_heart,
                                     sei = con_se_heart,
                                     ni = n_diab,
                                     measure = "OR",
                                     slab = name,
                                     method="REML",
                                     data = data_long_main)

```

```{r, echo=FALSE}
#save to output object for manuscript
save(list = c("data_cross_main", "data_long_main", 
               "meta.cross.hbp.con", "meta.cross.diab.con", "meta.cross.heart.con",
              "meta.long.hbp.con", "meta.long.diab.con", "meta.long.heart.con"), 
     file = "../meta output/main_conscientiousness.Rdata")
```

```{r forest, fig.height=15, echo = F}
con.data = data.frame(study = c(rep(data_cross_main$name, 3),rep(data_long_main$name, 3)),
                       outcome = c(rep("diabetes", nrow(data_cross_main)),
                                   rep("high blood pressure", nrow(data_cross_main)),
                                   rep("heart disease", nrow(data_cross_main)),
                                   rep("diabetes", nrow(data_long_main)),
                                   rep("high blood pressure", nrow(data_long_main)),
                                   rep("heart disease", nrow(data_long_main))),
                       model = c(rep("cross", nrow(data_cross_main)*3),
                                 rep("long", nrow(data_cross_main)*3)),
                       estimate = c(data_cross_main$con_est_diab,
                                    data_cross_main$con_est_hbp,
                                    data_cross_main$con_est_heart,
                                    data_long_main$con_est_diab,
                                    data_long_main$con_est_hbp,
                                    data_long_main$con_est_heart),
                       se = c(data_cross_main$con_se_diab,
                              data_cross_main$con_se_hbp,
                              data_cross_main$con_se_heart,
                              data_long_main$con_se_diab,
                              data_long_main$con_se_hbp,
                              data_long_main$con_se_heart),
                       n = c(data_cross_main$n_diab,
                             data_cross_main$n_hbp,
                             data_cross_main$n_heart,
                             data_long_main$n_diab,
                             data_long_main$n_hbp,
                             data_long_main$n_heart))

con.data = con.data %>%
  filter(!is.na(estimate)) %>%
  mutate(outcome = factor(outcome,
    levels = c("high blood pressure", "diabetes", "heart disease"))) %>%
  
  arrange(outcome, model, study)
#find plot limits

max.ci.mod1 = con.data %>%
  mutate(ci = exp(estimate+1.96*se)) %>%
  arrange(desc(ci))
max.ci.mod1 = max.ci.mod1[2, "ci"]

min.ci.mod1 = min(exp(con.data$estimate-1.96*con.data$se))

range.mod1 = max.ci.mod1-min.ci.mod1

lower.mod1 = min.ci.mod1-(range.mod1)
upper.mod1 = max.ci.mod1+(range.mod1)*.5

cex.value = .65

#estimate position of extra information
pos.mod1 = min.ci.mod1-lower.mod1
pos.mod1 = pos.mod1/2
pos.mod1 = c(lower.mod1+1*pos.mod1)

# rows
rows.heart.long = which(con.data$outcome == "heart disease" & con.data$model == "long")
rows.heart.long = c(1, length(rows.heart.long))

rows.heart.cross = which(con.data$outcome == "heart disease" & con.data$model == "cross")
rows.heart.cross = c(rows.heart.long[2] + 5, rows.heart.long[2] + 4 + length(rows.heart.cross))

rows.diabetes.long = which(con.data$outcome == "diabetes" & con.data$model == "long")
rows.diabetes.long = c(rows.heart.cross[2] + 5, rows.heart.cross[2] + 4 + length(rows.diabetes.long))

rows.diabetes.cross = which(con.data$outcome == "diabetes" & con.data$model == "cross")
rows.diabetes.cross = c(rows.diabetes.long[2] + 5, rows.diabetes.long[2] + 4 + length(rows.diabetes.cross))

rows.hbp.long = which(con.data$outcome == "high blood pressure" & con.data$model == "long")
rows.hbp.long = c(rows.diabetes.cross[2] + 5, rows.diabetes.cross[2] + 4 + length(rows.hbp.long))

rows.hbp.cross = which(con.data$outcome == "high blood pressure" & con.data$model == "cross")
rows.hbp.cross = c(rows.hbp.long[2] + 5, rows.hbp.long[2] + 4 + length(rows.hbp.cross))


#forest plot
forest(con.data$estimate, con.data$se^2,
       xlim = c(lower.mod1, upper.mod1),
       alim = c(min.ci.mod1, max.ci.mod1),
       cex = cex.value, slab = con.data$study,
       transf=exp,
       refline = 1,
       ylim = c(-1, max(rows.hbp.cross)+5),
       rows = c(rows.hbp.cross[2]:rows.hbp.cross[1],
                rows.hbp.long[2]:rows.hbp.long[1],
                rows.diabetes.cross[2]:rows.diabetes.cross[1],
                rows.diabetes.long[2]:rows.diabetes.long[1],
                rows.heart.cross[2]:rows.heart.cross[1],
                rows.heart.long[2]:rows.heart.long[1]),
       ilab = cbind(con.data$position),
       ilab.xpos = pos.mod1)

### add summary polygons
addpoly(meta.long.diab.con, row=rows.diabetes.long[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")
addpoly(meta.cross.diab.con, row=rows.diabetes.cross[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")
addpoly(meta.long.hbp.con, row=rows.hbp.long[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")
addpoly(meta.cross.hbp.con, row=rows.hbp.cross[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")
addpoly(meta.long.heart.con, row=rows.heart.long[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")
addpoly(meta.cross.heart.con, row=rows.heart.cross[1]-1, 
        cex = cex.value, transf =exp, mlab="", col = "blue")

### add text with Q-value, dfs, p-value, and I^2 statistic for subgroups
text(lower.mod1, rows.diabetes.long[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.long.diab.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.long.diab.con$k - meta.long.diab.con$p),
                  ", p = ", .(formatC(meta.long.diab.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.long.diab.con$I2, digits=1, format="f")), "%)")))
text(lower.mod1, rows.diabetes.cross[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.cross.diab.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.cross.diab.con$k - meta.cross.diab.con$p),
                  ", p = ", .(formatC(meta.cross.diab.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.cross.diab.con$I2, digits=1, format="f")), "%)")))
text(lower.mod1, rows.hbp.long[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.long.hbp.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.long.hbp.con$k - meta.long.hbp.con$p),
                  ", p = ", .(formatC(meta.long.hbp.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.long.hbp.con$I2, digits=1, format="f")), "%)")))
text(lower.mod1, rows.hbp.cross[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.cross.hbp.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.cross.hbp.con$k - meta.cross.hbp.con$p),
                  ", p = ", .(formatC(meta.cross.hbp.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.cross.hbp.con$I2, digits=1, format="f")), "%)")))
text(lower.mod1, rows.heart.long[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.long.heart.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.long.heart.con$k - meta.long.heart.con$p),
                  ", p = ", .(formatC(meta.long.heart.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.long.heart.con$I2, digits=1, format="f")), "%)")))
text(lower.mod1, rows.heart.cross[1]-1, pos=4, cex = cex.value,
     bquote(paste("(Q = ",
                  .(formatC(meta.cross.heart.con$QE, digits=2, format="f")),
                  ", df = ", .(meta.cross.heart.con$k - meta.cross.heart.con$p),
                  ", p = ", .(formatC(meta.cross.heart.con$QEp, digits=2, format="f")), "; ", I^2, " = ",
                  .(formatC(meta.cross.heart.con$I2, digits=1, format="f")), "%)")))

###additional text
text(lower.mod1, rows.hbp.cross[2] + 4,
     "Study", cex = cex.value, pos = 4)
text(upper.mod1, rows.hbp.cross[2] + 4,
     "Odds Ratio [95% CI]", cex = cex.value, pos=2)
text((lower.mod1+upper.mod1)/2, rows.hbp.cross[2] + 4,
     "Standardized coefficient of neuroticism", cex = cex.value)
text(lower.mod1, rows.diabetes.cross[2] + 1,
     "Diabetes (cross-sectional analyses)", cex = cex.value, pos = 4, font = 2)
text(lower.mod1, rows.diabetes.long[2] + 1,
     "Diabetes (longitudinal analyses)", cex = cex.value, pos = 4, font = 2)
text(lower.mod1, rows.hbp.cross[2] + 1,
     "High Blood Pressure (cross-sectional analyses)", cex = cex.value, pos = 4, font = 2)
text(lower.mod1, rows.hbp.long[2] + 1,
     "High Blood Pressure (longitudinal analyses)", cex = cex.value, pos = 4, font = 2)
text(lower.mod1, rows.heart.cross[2] + 1,
     "Heart Disease (cross-sectional analyses)", cex = cex.value, pos = 4, font = 2)
text(lower.mod1, rows.heart.long[2] + 1,
     "Heart Disease (longitudinal analyses)", cex = cex.value, pos = 4, font = 2)
```

# Code

The following packages were used to generate this figure: 

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

First we load the individual study analysis objects.

```{r load_data, warning=FALSE, message=FALSE, eval = F}
```

We extract the relevant statistics in a loop. (The first author is just learning how to use the `purrr` package, and so often resorts to loops when under a time constraint.)

We extract the coefficient estimates of conscientiousness and the standard errors for each study. We do this separately for the cross-sectional and longitudinal models, so there is one data frame for each.

```{r extra_info, eval = F}
```

Next, we use the tools of meta-analysis to estimate the weighted average effect and heterogeneity for each outcome.

```{r meta_analysis, eval = F}
```

Finally, we put the information into a single forest plot.

```{r forest, fig.height=15, eval = F}
```

