---
title: "Power analysis for heterogeneity in meta-analysis"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    theme: cosmo
---

This document contains the power analysis for the primary models of interest. For each model, we display the power to detect significant $\tau$ values, or different standard deviations of between-study effects (reported in the metric of odds ratios). We also mark the level of $tau$ estimated by our model and the power to detect this effect. We note here that we are well powered to detect between-study variability that is commonly found in psychology ([van Erp, Verhagen, Grasman, & Wagenmakers, 2017](https://openpsychologydata.metajnl.com/articles/10.5334/jopd.33/)).

Many thanks to Brenton Wiernik, who developed the code to calculate power based on our analyses!

```{r function, echo = F}
# Based on methods described by Hedges and Pigott, https://doi.org/10.1037/1082-989X.9.4.426, p. 438
# Written 2019-10-25 by Brenton M. Wiernik
# Licensed GPL v3.0

power_curve <- function(object, tau, level = .95) {
  if (! inherits(object, "rma.uni")) stop("'object' must be an object of class 'rma.uni'")
  tau2 <- tau^2
  obs_tau2 <- object$tau2
  obs_tau <- sqrt(obs_tau2)
  obs_H2 <- object$H2
  s2 <- obs_tau2 / (obs_H2 - 1)
  df <- object$k - object$p
  crit <- qchisq(.95, df)
  wi <- 1 / object$vi
  a <- sum(wi) - sum(wi^2) / sum(wi)
  mu_q <- function(tau2) a * tau2 + df
  b <- function(tau2) df + 2 * a * tau2 + 
    (sum(wi^2) - 2 * sum(wi^3) / sum(wi) + 
       sum(wi^2)^2 / sum(wi)^2) * tau2^2
  var_q <- function(tau2) 2 * b(tau2)
  r <- function(tau2) var_q(tau2) / (2 * mu_q(tau2))
  s <- function(tau2) 2 * mu_q(tau2)^2 / var_q(tau2)
  H <- function(tau2) pchisq(crit / r(tau2), s(tau2))
  power <- 1 - H(tau2)
  out <- list(obs_tau = obs_tau, power = data.frame(tau = tau, power = power))
  return(out)
}
```

The following packages were used to generate this figure: 

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide', echo = F}
library(tidyverse)
library(metafor)
library(papaja)
library(here)
```

```{r tau, echo = F}
tau = seq(0, .5, .01) # possible values of the standard deviation of effect sizes
```


# Cross-sectional

## Hypertension/high blood pressure

```{r cross_hbp, echo = F}
load(here("meta output/hbp_cross.Rdata"))

power_hbp_cross = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_hbp_cross$obs_tau, level =.95)$power[1,2]

#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_hbp_cross$power$power-pwr.95)==min(abs(power_hbp_cross$power$power-pwr.95)))
pwr.95 = power_hbp_cross$power$power[tau.95]
tau.95 = power_hbp_cross$power$tau[tau.95]
tau.99 = which(abs(power_hbp_cross$power$power-pwr.99)==min(abs(power_hbp_cross$power$power-pwr.99)))
pwr.99 = power_hbp_cross$power$power[tau.99]
tau.99 = power_hbp_cross$power$tau[tau.99]

power_hbp_cross$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_hbp_cross$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_hbp_cross$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_hbp_cross$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in cross-sectional hypertension models") +
  theme_bw()


```

## Diabetes

```{r cross_diab, echo = F}
load(here("meta output/diabetes_cross.Rdata"))

power_diabetes_cross = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_diabetes_cross$obs_tau, level =.95)$power[1,2]

#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_diabetes_cross$power$power-pwr.95)==min(abs(power_diabetes_cross$power$power-pwr.95)))
pwr.95 = power_diabetes_cross$power$power[tau.95]
tau.95 = power_diabetes_cross$power$tau[tau.95]
tau.99 = which(abs(power_diabetes_cross$power$power-pwr.99)==min(abs(power_diabetes_cross$power$power-pwr.99)))
pwr.99 = power_diabetes_cross$power$power[tau.99]
tau.99 = power_diabetes_cross$power$tau[tau.99]

power_diabetes_cross$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_diabetes_cross$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_diabetes_cross$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_diabetes_cross$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in cross-sectional hypertension models") +
  theme_bw()


```


## Heart disease

```{r cross_heart, echo = F}
load(here("meta output/heart_cross.Rdata"))

power_heart_cross = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_heart_cross$obs_tau, level =.95)$power[1,2]
#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_heart_cross$power$power-pwr.95)==min(abs(power_heart_cross$power$power-pwr.95)))
pwr.95 = power_heart_cross$power$power[tau.95]
tau.95 = power_heart_cross$power$tau[tau.95]
tau.99 = which(abs(power_heart_cross$power$power-pwr.99)==min(abs(power_heart_cross$power$power-pwr.99)))
pwr.99 = power_heart_cross$power$power[tau.99]
tau.99 = power_heart_cross$power$tau[tau.99]

power_heart_cross$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_heart_cross$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_heart_cross$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_heart_cross$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in cross-sectional hypertension models") +
  theme_bw()
```

# Longitudinal

## Hypertension/high blood pressure

```{r long_hbp, echo = F}
load(here("meta output/hbp_long.Rdata"))

power_hbp_long = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_hbp_long$obs_tau, level =.95)$power[1,2]

#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_hbp_long$power$power-pwr.95)==min(abs(power_hbp_long$power$power-pwr.95)))
pwr.95 = power_hbp_long$power$power[tau.95]
tau.95 = power_hbp_long$power$tau[tau.95]
tau.99 = which(abs(power_hbp_long$power$power-pwr.99)==min(abs(power_hbp_long$power$power-pwr.99)))
pwr.99 = power_hbp_long$power$power[tau.99]
tau.99 = power_hbp_long$power$tau[tau.99]

power_hbp_long$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_hbp_long$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_hbp_long$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_hbp_long$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in longitudinal hypertension models") +
  theme_bw()


```

## Diabetes

```{r long_diab, echo = F}
load(here("meta output/diabetes_long.Rdata"))

power_diabetes_long = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_diabetes_long$obs_tau, level =.95)$power[1,2]

#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_diabetes_long$power$power-pwr.95)==min(abs(power_diabetes_long$power$power-pwr.95)))
pwr.95 = power_diabetes_long$power$power[tau.95]
tau.95 = power_diabetes_long$power$tau[tau.95]
tau.99 = which(abs(power_diabetes_long$power$power-pwr.99)==min(abs(power_diabetes_long$power$power-pwr.99)))
pwr.99 = power_diabetes_long$power$power[tau.99]
tau.99 = power_diabetes_long$power$tau[tau.99]

power_diabetes_long$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_diabetes_long$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_diabetes_long$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_diabetes_long$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in longitudinal hypertension models") +
  theme_bw()


```


## Heart disease

```{r long_heart, echo = F}
load(here("meta output/heart_long.Rdata"))

power_heart_long = power_curve(meta.int.mod3, tau, level = .95)
obs = power_curve(meta.int.mod3, power_heart_long$obs_tau, level =.95)$power[1,2]

#for which tau are we powered?
pwr.95=.95
pwr.99=.99
tau.95 = which(abs(power_heart_long$power$power-pwr.95)==min(abs(power_heart_long$power$power-pwr.95)))
pwr.95 = power_heart_long$power$power[tau.95]
tau.95 = power_heart_long$power$tau[tau.95]
tau.99 = which(abs(power_heart_long$power$power-pwr.99)==min(abs(power_heart_long$power$power-pwr.99)))
pwr.99 = power_heart_long$power$power[tau.99]
tau.99 = power_heart_long$power$tau[tau.99]

power_heart_long$power %>%
  mutate(tau_d = tau/(pi/sqrt(3))) %>%
  ggplot(aes(x = tau_d, y = power)) +
  geom_point()+
  geom_line()+
  geom_vline(aes(xintercept = power_heart_long$obs_tau/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.95/(pi/sqrt(3))), color = "red") +
  geom_vline(aes(xintercept = tau.99/(pi/sqrt(3))), color = "red") +
  geom_label(aes(x = power_heart_long$obs_tau, y = obs, 
                 label = paste("power =", round(obs, 3), 
                               "\ntau = ", round( power_heart_long$obs_tau/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.95/(pi/sqrt(3)), y = pwr.95-.3, 
                 label = paste("power =", round(pwr.95, 3), 
                               "\ntau = ", round( tau.95/(pi/sqrt(3)), 3))), hjust = "inward")+
  geom_label(aes(x = tau.99/(pi/sqrt(3)), y = pwr.99-.15, 
                 label = paste("power =", round(pwr.99, 3), 
                               "\ntau = ", round( tau.99/(pi/sqrt(3)), 3))), hjust = "inward")+
  labs(x = "Standard deviation of Odds Ratios between studies", 
       y = "Power | alpha = .05",
       title = "Power analyses interaction term in longitudinal hypertension models") +
  theme_bw()
```

# Code

```{r ref.label = "function", eval = F}
```

The following packages were used to generate this figure: 

```{r ref.label = "load_packages", warning = FALSE, message = FALSE, results = 'hide', eval = F}
```

```{r ref.label = "tau", eval = F}
```


## Cross-sectional

### Hypertension/high blood pressure

```{r ref.label = "cross_hbp", eval = F}
```

### Diabetes

```{r ref.label = "cross_diab", eval = F}
```


### Heart disease

```{r ref.label = "cross_heart", eval = F}
```

## Longitudinal

### Hypertension/high blood pressure

```{r ref.label = "long_hbp", eval = F}
```

### Diabetes

```{r ref.label = "long_diab", eval = F}
```


### Heart disease

```{r ref.label = "long_heart", eval = F}
```

