---
title: "meta_age.sex"

output: html_document
---
This document contains the meta-analysis of the surivival models, using age.sex since baseline as the metric of interest and neuroticism by conscientiousness as the predictor of interest.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

The following packages were used to generate this table: 

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide'}
library(papaja)
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
```

Specify the location of the study analysis objects. The first author stored these in a Box Sync folder, but you may have downloaded these to a different location. The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

```{r}
data.path = c("../study output/")
```

First we load the individual study analysis objects.

```{r, results = 'hide'}
study.names = c("EAS", "HRS", "LBC", "LBLS", "MAP", "MAS", "MIDUS", "OATS", "ROS", "SLS", "WLS")

lapply(paste0(data.path, study.names, "_survival_output.Rdata"), load, .GlobalEnv)
```


```{r}
meta.data.age.sex <- data.frame()
n <- 0

for(i in study.names){
  n <- n+1
  x <- get(paste0(i, "_survival_output"))
  meta.data.age.sex[n, "study"] <- i
  meta.data.age.sex[n, "coef"] <- x$age$model3$coef["z.neur:z.con", "coef"]
  meta.data.age.sex[n, "se"] <- x$age$model3$coef["z.neur:z.con", "se(coef)"]
  meta.data.age.sex[n, "n"] <- x$age$model3$ntotal
  
  meta.data.age.sex[n, "lowC.male.est"] <- x$HR.N$age.sex$LowC.male$est
  meta.data.age.sex[n, "lowC.male.se"] <- x$HR.N$age.sex$LowC.male$se
  meta.data.age.sex[n, "hghC.male.est"] <- x$HR.N$age.sex$HghC.male$est
  meta.data.age.sex[n, "hghC.male.se"] <- x$HR.N$age.sex$HghC.male$se
  
  meta.data.age.sex[n, "lowC.female.est"] <- x$HR.N$age.sex$LowC.female$est
  meta.data.age.sex[n, "lowC.female.se"] <- x$HR.N$age.sex$LowC.female$se
  meta.data.age.sex[n, "hghC.female.est"] <- x$HR.N$age.sex$HghC.female$est
  meta.data.age.sex[n, "hghC.female.se"] <- x$HR.N$age.sex$HghC.female$se
  
  #calculate hazard ratios at low and high C
  lowC.male.HR <- exp(x$HR.N$age.sex$LowC.male$est)
  lowC.male.HR.lwr <- exp(x$HR.N$age.sex$LowC.male$est - 1.96*x$HR.N$age.sex$LowC.male$se)
  lowC.male.HR.upr <- exp(x$HR.N$age.sex$LowC.male$est + 1.96*x$HR.N$age.sex$LowC.male$se)
  meta.data.age.sex[n, "lowC.male.CI"] <- paste0(printnum(lowC.male.HR)," [",printnum(lowC.male.HR.lwr),", ",printnum(lowC.male.HR.upr),"]")

  hghC.male.HR <- exp(x$HR.N$age.sex$HghC.male$est)
  hghC.male.HR.lwr <- exp(x$HR.N$age.sex$HghC.male$est - 1.96*x$HR.N$age.sex$HghC.male$se)
  hghC.male.HR.upr <- exp(x$HR.N$age.sex$HghC.male$est + 1.96*x$HR.N$age.sex$HghC.male$se)
  meta.data.age.sex[n, "hghC.male.CI"] <- paste0(printnum(hghC.male.HR),
                                                  " [",printnum(hghC.male.HR.lwr),", ",
                                                  printnum(hghC.male.HR.upr),"]")
  
  lowC.female.HR <- exp(x$HR.N$age.sex$LowC.female$est)
  lowC.female.HR.lwr <- exp(x$HR.N$age.sex$LowC.female$est - 1.96*x$HR.N$age.sex$LowC.female$se)
  lowC.female.HR.upr <- exp(x$HR.N$age.sex$LowC.female$est + 1.96*x$HR.N$age.sex$LowC.female$se)
  meta.data.age.sex[n, "lowC.female.CI"] <- paste0(printnum(lowC.female.HR),
                                                   " [",printnum(lowC.female.HR.lwr),", ",printnum(lowC.female.HR.upr),"]")

  hghC.female.HR <- exp(x$HR.N$age.sex$HghC.female$est)
  hghC.female.HR.lwr <- exp(x$HR.N$age.sex$HghC.female$est - 1.96*x$HR.N$age.sex$HghC.female$se)
  hghC.female.HR.upr <- exp(x$HR.N$age.sex$HghC.female$est + 1.96*x$HR.N$age.sex$HghC.female$se)
  meta.data.age.sex[n, "hghC.female.CI"] <- paste0(printnum(hghC.female.HR),
                                                   " [",printnum(hghC.female.HR.lwr),", ",printnum(hghC.female.HR.upr),"]")

}

meta.results.age.sex <- rma(yi = coef, 
                    sei = se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age.sex)
```

```{r}
#meta-analyze HR at low and high c

meta.lowmale.age.sex <- rma(yi = lowC.male.est, 
                    sei = lowC.male.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age.sex)

meta.hghmale.age.sex <- rma(yi = hghC.male.est, 
                    sei = hghC.male.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age.sex)

meta.lowfemale.age.sex <- rma(yi = lowC.female.est, 
                    sei = lowC.female.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age.sex)

meta.hghfemale.age.sex <- rma(yi = hghC.female.est, 
                    sei = hghC.female.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age.sex)


#find plot limits
max.ci.mod1 = max(exp(meta.data.age.sex$coef+1.96*meta.data.age.sex$se))
min.ci.mod1 = min(exp(meta.data.age.sex$coef-1.96*meta.data.age.sex$se))
range.mod1 = max.ci.mod1-min.ci.mod1

lower.mod1 = min.ci.mod1-(range.mod1*7)
upper.mod1 = max.ci.mod1+(range.mod1*1.5)

cex.set = .7

#estimate position of extra information
pos.mod1 = min.ci.mod1-lower.mod1
pos.mod1 = pos.mod1/15
pos.mod1 = c(lower.mod1+3*pos.mod1,
             lower.mod1+5*pos.mod1,
             lower.mod1+7.5*pos.mod1,
             lower.mod1+10.5*pos.mod1,
             lower.mod1+13*pos.mod1)

#extract weighted values at -1 and +1 sd
meta_est_lowc_male_mod1 = printnum(exp(meta.lowmale.age.sex$b))
meta_lwr_lowc_male_mod1 = printnum(exp(meta.lowmale.age.sex$ci.lb))
meta_upr_lowc_male_mod1 = printnum(exp(meta.lowmale.age.sex$ci.ub))
meta_lowc_male_ci_mod1 = paste0(meta_est_lowc_male_mod1, " [",
                           meta_lwr_lowc_male_mod1, ", ",
                           meta_upr_lowc_male_mod1, "]")

meta_est_hghc_male_mod1 = printnum(exp(meta.hghmale.age.sex$b))
meta_lwr_hghc_male_mod1 = printnum(exp(meta.hghmale.age.sex$ci.lb))
meta_upr_hghc_male_mod1 = printnum(exp(meta.hghmale.age.sex$ci.ub))
meta_hghc_male_ci_mod1 = paste0(meta_est_hghc_male_mod1, " [",
                           meta_lwr_hghc_male_mod1, ", ",
                           meta_upr_hghc_male_mod1, "]")

meta_est_lowc_female_mod1 = printnum(exp(meta.lowfemale.age.sex$b))
meta_lwr_lowc_female_mod1 = printnum(exp(meta.lowfemale.age.sex$ci.lb))
meta_upr_lowc_female_mod1 = printnum(exp(meta.lowfemale.age.sex$ci.ub))
meta_lowc_female_ci_mod1 = paste0(meta_est_lowc_female_mod1, " [",
                           meta_lwr_lowc_female_mod1, ", ",
                           meta_upr_lowc_female_mod1, "]")

meta_est_hghc_female_mod1 = printnum(exp(meta.hghfemale.age.sex$b))
meta_lwr_hghc_female_mod1 = printnum(exp(meta.hghfemale.age.sex$ci.lb))
meta_upr_hghc_female_mod1 = printnum(exp(meta.hghfemale.age.sex$ci.ub))
meta_hghc_female_ci_mod1 = paste0(meta_est_hghc_female_mod1, " [",
                           meta_lwr_hghc_female_mod1, ", ",
                           meta_upr_hghc_female_mod1, "]")

```
```{r, fig.width=8}
#forest plot
meta.data.age.sex$study = gsub("LBC", "LBC1936", meta.data.age.sex$study)

forest(meta.results.age.sex,
       xlim = c(lower.mod1, upper.mod1),
       cex = cex.set,
       slab = meta.data.age.sex$study,
       transf=exp,
       refline = 1,
       ilab = meta.data.age.sex[,c("n",
                                "lowC.male.CI",
                                "hghC.male.CI",
                                "lowC.female.CI",
                                "hghC.female.CI")],
       ilab.xpos = pos.mod1)

# #additional text
text(pos.mod1[1], length(study.names)+1.5,
     c("N"), cex = cex.set)
text(pos.mod1[2], length(study.names)+1.5,
     c("Low Con"), cex = cex.set)
text(pos.mod1[3], length(study.names)+1.5,
     c("High Con"), cex = cex.set)
text(pos.mod1[4], length(study.names)+1.5,
     c("Low Con"), cex = cex.set)
text(pos.mod1[5], length(study.names)+1.5,
     c("High Con"), cex = cex.set)
text((pos.mod1[2]+pos.mod1[3])/2, length(study.names)+2.5,
     c("Male"), cex = cex.set)
text((pos.mod1[4]+pos.mod1[5])/2, length(study.names)+2.5,
     c("Female"), cex = cex.set)

text((pos.mod1[3]+pos.mod1[4])/2, length(study.names)+3,
     "Neuroticism Hazard Ratio", cex = cex.set)

text(lower.mod1, length(study.names)+1.5,
     "Study", cex = cex.set, pos = 4)
text(upper.mod1, length(study.names)+1.5,
     "Interaction Hazard Ratio [95% CI]", cex = cex.set, pos=2)
text(pos.mod1[2:5], -1,
     c(meta_lowc_male_ci_mod1, meta_hghc_male_ci_mod1, 
       meta_lowc_female_ci_mod1, meta_hghc_female_ci_mod1), cex = cex.set)
text(lower.mod1, -2, pos=4, cex=cex.set,
     bquote(paste("(Q = ",
     .(formatC(meta.results.age.sex$QE, digits=2, format="f")),
     ", df = ", .(meta.results.age.sex$k - meta.results.age.sex$p),
     ", p = ", .(formatC(meta.results.age.sex$QEp, digits=2, format="f")),
     "; ", I^2, " = ",
     .(formatC(meta.results.age.sex$I2, digits=1, format="f")), "%)")))

```