---
title: "Supplementary: Meta analysis of interaction (age as metric)"

output: html_document
---
This document contains the meta-analysis of the surivival models, using age in years as the metric of interest and neuroticism by conscientiousness as the predictor of interest.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

The following packages were used to generate this table: 

```{r load_packages, warning = FALSE, message = FALSE, results = 'hide'}
library(papaja)
library(tidyverse)
library(metafor)
library(knitr)
library(kableExtra)
```

Specify the location of the study analysis objects. The first author stored these in a Box Sync folder, but you may have downloaded these to a different location. The files needed for this table are available at [osf.io/mzfu9](https://osf.io/mzfu9/) in the Individual Study Output folder.

```{r}
data.path = c("../study output/")
```

First we load the individual study analysis objects.

```{r, results = 'hide'}
study.names = c("EAS", "HRS", "LBC", "LBLS", "MAP", "MAS", "MIDUS", "NAS", "OATS", "ROS", "SLS", "WLS")

lapply(paste0(data.path, study.names, "_survival_output.Rdata"), load, .GlobalEnv)
```


```{r}
meta.data.age <- data.frame()
n <- 0

for(i in study.names){
  n <- n+1
  x <- get(paste0(i, "_survival_output"))
  meta.data.age[n, "study"] <- i
  meta.data.age[n, "coef"] <- x$age$model2$coef["z.neur:z.con", "coef"]
  meta.data.age[n, "se"] <- x$age$model2$coef["z.neur:z.con", "se(coef)"]
  meta.data.age[n, "n"] <- x$age$model2$ntotal
  
  meta.data.age[n, "lowC.est"] <- x$HR.N$age$LowC$est
  meta.data.age[n, "lowC.se"] <- x$HR.N$age$LowC$se
  meta.data.age[n, "hghC.est"] <- x$HR.N$age$HghC$est
  meta.data.age[n, "hghC.se"] <- x$HR.N$age$HghC$se
  
  #calculate hazard ratios at low and high C
  lowC.HR <- exp(x$HR.N$age$LowC$est)
  lowC.HR.lwr <- exp(x$HR.N$age$LowC$est - 1.96*x$HR.N$age$LowC$se)
  lowC.HR.upr <- exp(x$HR.N$age$LowC$est + 1.96*x$HR.N$age$LowC$se)
  meta.data.age[n, "lowC.CI"] <- paste0(printnum(lowC.HR)," [",printnum(lowC.HR.lwr),", ",printnum(lowC.HR.upr),"]")

  hghC.HR <- exp(x$HR.N$age$HghC$est)
  hghC.HR.lwr <- exp(x$HR.N$age$HghC$est - 1.96*x$HR.N$age$HghC$se)
  hghC.HR.upr <- exp(x$HR.N$age$HghC$est + 1.96*x$HR.N$age$HghC$se)
  meta.data.age[n, "hghC.CI"] <- paste0(printnum(hghC.HR)," [",printnum(hghC.HR.lwr),", ",printnum(hghC.HR.upr),"]")

}

meta.results.age <- rma(yi = coef, 
                    sei = se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age)
```

```{r}
#meta-analyze HR at low and high c

meta.low.age <- rma(yi = lowC.est, 
                    sei = lowC.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age)

meta.hgh.age <- rma(yi = hghC.est, 
                    sei = hghC.se, 
                    ni = n,  
                    measure = "RR",
                    slab = study, 
                    data = meta.data.age)


#find plot limits
max.ci.mod1 = max(exp(meta.data.age$coef+1.96*meta.data.age$se))
min.ci.mod1 = min(exp(meta.data.age$coef-1.96*meta.data.age$se))
range.mod1 = max.ci.mod1-min.ci.mod1

lower.mod1 = min.ci.mod1-(range.mod1*2.5)
upper.mod1 = max.ci.mod1+(range.mod1)

cex.set = .7

#estimate position of extra information
pos.mod1 = min.ci.mod1-lower.mod1
pos.mod1 = pos.mod1/11
pos.mod1 = c(lower.mod1+3*pos.mod1,
             lower.mod1+6*pos.mod1,
             lower.mod1+9*pos.mod1)

#extract weighted values at -1 and +1 sd
meta_est_lowc_mod1 = printnum(exp(meta.low.age$b))
meta_lwr_lowc_mod1 = printnum(exp(meta.low.age$ci.lb))
meta_upr_lowc_mod1 = printnum(exp(meta.low.age$ci.ub))
meta_lowc_ci_mod1 = paste0(meta_est_lowc_mod1, " [",
                           meta_lwr_lowc_mod1, ", ",
                           meta_upr_lowc_mod1, "]")

meta_est_hghc_mod1 = printnum(exp(meta.hgh.age$b))
meta_lwr_hghc_mod1 = printnum(exp(meta.hgh.age$ci.lb))
meta_upr_hghc_mod1 = printnum(exp(meta.hgh.age$ci.ub))
meta_hghc_ci_mod1 = paste0(meta_est_hghc_mod1, " [",
                           meta_lwr_hghc_mod1, ", ",
                           meta_upr_hghc_mod1, "]")

meta.data.age$study = gsub("LBC", "LBC1936", meta.data.age$study)

#forest plot
forest(meta.results.age,
       xlim = c(lower.mod1, upper.mod1),
       slab = meta.data.age$study,
       cex = cex.set,
       transf=exp,
       refline = 1,
       ilab = meta.data.age[,c("n",
                                "lowC.CI",
                                "hghC.CI")],
       ilab.xpos = pos.mod1)

#additional text
text(c(pos.mod1), length(study.names)+1.5,
     c("N", "-1SD Con", "+1SD Con"), cex = cex.set)
text((pos.mod1[2]+pos.mod1[3])/2, length(study.names)+2.5,
     "Neuroticism Hazard Ratio", cex = cex.set)
text(lower.mod1, length(study.names)+1.5,
     "Study", cex = cex.set, pos = 4)
text(upper.mod1, length(study.names)+1.5,
     "Interaction Hazard Ratio [95% CI]", cex = cex.set, pos=2)
text(pos.mod1[2:3], -1,
     c(meta_lowc_ci_mod1, meta_hghc_ci_mod1), cex = cex.set)
text(lower.mod1, -2, pos=4, cex=cex.set, 
     bquote(paste("(Q = ",
     .(formatC(meta.results.age$QE, digits=2, format="f")), ", df = ", .(meta.results.age$k - meta.results.age$p),
     ", p = ", .(formatC(meta.results.age$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(meta.results.age$I2, digits=1, format="f")), "%)")))

```